Predicting computational reproducibility of data analysis pipelines \\in large population studies using collaborative filtering

### 2018-08-13 paper.tex
Added comment

\author{Soudabeh Barghi, Lalet Scaria, Tristan Glatard\\
  Department of Computer Science and Software Engineering\\ Concordia University, Montreal, Quebec, Canada\\
  {first.last}@concordia.ca}

@@

Figure~\ref{fig:roc} compares the sampling methods in the ROC space, 
for a training ratio of 0.9, on the synthetic and Freesurfer dataset. 
The PreFreesurfer dataset is not included since specificity of RFNTL, 
RFNU, RS and complete rows is undefined at this training ratio (the 
test set only contains positive elements \todo{Soudabeh: check matrix to confirm}). The average sensitivity and specificity values 
are reported in Table~\ref{table:roc}, which confirms that RFNU is the best 
performing method on average.

@@

@@

>>>>

\author{Soudabeh Barghi, Lalet Scaria, Tristan Glatard\\
  Department of Computer Science and Software Engineering\\ Concordia University, Montreal, Quebec, Canada\\
  {first.last}@concordia.ca \vspace*{-0.5cm}}

@@

Figure~\ref{fig:roc} compares the sampling methods in the ROC space, 
for a training ratio of 0.9, on the synthetic and Freesurfer dataset. 
The PreFreesurfer dataset is not included since specificity of RFNTL, 
RFNU, RS and complete rows is undefined at this training ratio (the 
test set only contains positive elements). The average sensitivity and specificity values 
are reported in Table~\ref{table:roc}, which confirms that RFNU is the best 
performing method on average.

@@

 \note{Soudabeh, add figure with two 3D plots showing the 3 factors of 
 every item and subject. Comment: the method indeed separates files in 
 3 blocks (for 8 types) and subjects in 8 types.}

@@

\todo{publish code on zenodo}
